Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-13 slides/slides.Rmd
made a plot prettier

scatterplot3d::scatterplot3d(X[, 1], X[, 2], X[, 3],
                             color = z, 
                             xlab = NA, ylab = NA, zlab = NA,
                             pch = '.', asp = 1,
                             tick.marks = FALSE)

scatterplot3d::scatterplot3d(Xhat[, 1], Xhat[, 2], Xhat[, 3], 
                             color = z, 
                             xlab = NA, ylab = NA, zlab = NA, 
                             pch = '.', asp = 1, 
                             tick.marks = FALSE,
                             angle = 40)
```

>>>>

scatterplot3d::scatterplot3d(X[, 1], X[, 2], X[, 3],
                             color = z, 
                             xlab = NA, ylab = NA, zlab = NA,
                             # pch = '.', 
                             asp = 1,
                             tick.marks = FALSE,
                             mar = c(0, 0, 0, 0))

scatterplot3d::scatterplot3d(Xhat[, 1], Xhat[, 2], Xhat[, 3], 
                             color = z, 
                             xlab = NA, ylab = NA, zlab = NA, 
                             # pch = '.', 
                             asp = 1, 
                             tick.marks = FALSE,
                             angle = 40,
                             mar = c(0, 0, 0, 0))
```
